\cvsection{Experience}
\begin{cventries}
	\cventry
	{Intern} % Job title
	{NOV} % Organization
	{Houston, USA} % Location
	{Feburary 2019 - May 2019} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item { Development of IoT application for next generation of SCADA to test new product line for internal customers.	} 
			\item { Collaborating with different department to understand existing control system upgrade and test IoT application services to work seamlessly with existing communication protocol (Serial, Modbus,  Modbus TCP/IP) }
		\end{cvitems}
	}

\end{cventries}
\begin{cventries}
	\cventry
	{Instructional Assistant for Sensors and Applications} % Job title
	{University of Houston} % Organization
	{College of Technology, Houston} % Location
	{January 2018 - Present} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Mentored undergraduate students to ensure laboratory experiments and course project are completed as per university's guidelines.} 
			\item {Collaborated with faculty to prepare coursework, laboratory manuals, and sessions as well as assignments and lab reports. }
		\end{cvitems}
	}

\end{cventries}

\begin{cventries}
	\cventry
	{ICSS (Integrated Control and Safety Systems) Engineer} % Job title
	{Daewoo Shipbuilding \& Marine Engineering} % Organization
	{Geoje, South Korea} % Location
	{February 2013 - March 2017} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Executed design, oversaw construction and supported commissioning of Hull/Topsides Distributed Control Systems, Fire, Gas Systems (FGS) and Emergency Shutdown Systems (ESD) compliant with marine class, International Standards and client specification for offshore oil and gas facilities.}
			\item {Collaborated with multi-disciplinary engineering team for preparing FPSO functional safety management and safety life cycle design documentation in compliance with IEC 61508 and 61511 to expedite project commissioning schedule.}
			\item {Coordinated engineering inputs and produced detail engineering design for Fire water pump and HVAC package fire damper control logic, including various safety studies such as electrical isolation, FGS mapping procedures, mapping studies, fire risk and gas dispersion study.}
			\item {Performed construction survey to ensure Hull and Topsides FGS detector location and coverage is compliant with mapping study requirement.}
			\item {Led team of one engineer and two designers to design instrument layout, instrument construction details and cable layouts drawings.}
			\item {Executed design of control system cabinet, I/O list, electrical schematic, single line, Junction box schedule, cable schedule, cause \& effect, functional specification and control narratives.}		
		\end{cvitems}
	}
	\cvprojentry
	{Project : }
	{Ichthys FPSO}
\end{cventries}

\begin{cventries}
	\cventry
	{\textbf{Control System Engineer}} % Job title
	{Emerson Export Engineering Centre} % Organization
	{Pune, India} % Location
	{\textbf{December 2010 - February 2013}} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Managed onshore and offshore facilities control/safety systems hardware/software engineering and integrated hardware/software tests with the package vendor, Engineering, Procurement and Construction Company (EPC) and client.}
			\item {Assisted EPC in the development of control and safety systems functional analysis for time-bound Factory Acceptance Test (FAT) schedule to meet EPC construction targets, whilst managing client comments and software modifications to ensure quality assurance.}
			\item {Site commissioning leader for SHELL technologies and Saudi Aramco to design, install and commission control systems for onshore hydrocarbon facilities adhering to SHELL and Saudi Aramco HSE practices.}
		\end{cvitems}
	}
	\cvprojentry
	{Project : }
	{Shell Deer Park, Shell Technologies, Hawatah Saudi Aramco, Total E \& P CLOV FPSO, Dow Chemicals}
\end{cventries}

\begin{cventries}
	\cventry
	{Instrument Engineer} % Job title
	{Biocon Ltd} % Organization
	{Bangalore, India} % Location
	{August 2010 - December 2010} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Ensure maximum production by executing all operation and maintenance aspects of pharma plant to ensure maximum production availability of control systems and field instruments. }
			\item {Organized preventive maintenance schedule and managed inventory. }
			\item {Oversaw risk assessment team to ensure safety aspect of operation.}	
		\end{cvitems}
	}

\end{cventries}

\begin{cventries}
	\cventry
	{Instrument Engineer} % Job title
	{Laksel EPS Technologies Pte Ltd.} % Organization
	{Mumbai, India} % Location
	{Octomber 2009 - August 2010} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item { Assisted Lead Instrument and Process engineer for the installation, hook-up and commissioning of field instrumentation and control systems of 3 phase crude oil separators whilst adhering to client HSE practices.} 
			\item { Coordinated with plant operation team for troubleshooting and preventive maintenance of field Instruments until the stabilization of the hydrocarbon plant.}
		\end{cvitems}
	}
	\cvprojentry
	{Project : }
	{Petrodar Co-operating Company}
\end{cventries}

\begin{cventries}
	\cventry
	{Project Engineer} % Job title
	{Emerson Process Management PVT. LTD} % Organization
	{Mumbai, India} % Location
	{July 2008 - Octomber 2009} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Coordinated with EPC and Operator for graphics design, Control systems networking, Cabinet hardware design and software programming to ensure successful FAT. }
			\item {Oversaw cabinet installation, executed commissioning and start-up of process plant to ensure control system hardware and software quality assurance.}
			\item {Delivered quality assurance by ensuring pressure, temperature and flow instruments are calibrated within accuracy tolerance. }
			\item {Datasheet and functional specification for pressure, temperature and flow instruments. }	
		\end{cvitems}
	}
		\cvprojentry
	{Project : }
	{Indian Oil Refinery(IOCL) Baroda, Indian Oil Refinery(IOCL) Baruni}
\end{cventries}

