\cvsection{Experience}
\begin{cventries}
	\cventry
	{Graduate Assistant} % Job title
	{Information Technology Services} % Organization
	{Prairie View A\&M University, USA} % Location
	{June 2016 - Aug 2016, Aug 2017- Present} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item { \textbf{Co-admin} support for on-campus users providing \textbf{Cisco Unified Communication and Networking} solutions. Data analysis on Cisco  database to get provide maintainance insigthts. Providing excellent installation and technical support: hardware/software across the whole campus.}  
			\item {Developing reports for security audits on the databases using SQL Workbench on python. Coordinating with the Information and Technology Service team and reporting the security issues. Documentation of the technical services.}
		\end{cvitems}
	}
\end{cventries}
\begin{cventries}
	\cventry
	{Graduate Research Assistant - Thesis} % Job title
	{Center of excellence in Research and Education for big military Data InTelligence (CREDIT)} % Organization
	{Prairie View A\&M University, USA} % Location
	{September 2016 - July 2017 - Present} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Build Deep Learning regression models on Smart Meter Data from Irish Social Science Data Archive to forecast power usage based on individual consumer driven to facilitate the electric utility company and consumers to forecast energy demand to use energy most efficiently and save energy loss.}
			\item {Build multi-class classifier to classify which plan fits best based on their energy usage behavior using Keras Deep Learning.}
			\item {Successfully supervised and guided undergraduate students in building a "Portable Air Quality Device" using Arduino.}
		\end{cvitems}
	}
\end{cventries}

\begin{cventries}
	\cventry
	{Graduate Research Assistant and Tutor} % Job title
	{Center for Energy and Environment Sustainability and Naval Reserve Officers Training Corps} % Organization
	{Prairie View A\&M University, USA} % Location
	{October 2015 - May 2016} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Amass research papers based on Life Cycle Assessment of Energy generated from different sources such as coal energy, nuclear energy, geothermal energy, wind energy. Houston-area Air Quality Data processing and formatting on Excel programming.}
			\item {Succeeded in raising student's grade from a 60\% to 90\% to secure NROTC Scholarship. Provided tutoring for physics \& mathematics courses.}
		\end{cvitems}
	}
\end{cventries}
%\begin{cventries}
%	\cventry
%	{Tutor} % Job title
%	{Naval Reserve Officers Training Corps (NROTC)} % Organization
%	{Prairie View A\&M University, USA} % Location
%	{October 2015 - May 2016} % Date(s)
%	{ % Description(s) of tasks/responsibilities
%		\begin{cvitems}	
%		\end{cvitems}
%	}
%\end{cventries}
\begin{cventries}
	\cventry
	{Quality and Test Engineer for Power and Distribution Transformer} % Job title
	{Patel Electricals} % Organization
	{Waghodia, India} % Location
	{July 2012 - July 2015} % Date(s)
	{ % Description(s) of tasks/responsibilities
		\begin{cvitems}
			\item {Inspection of incoming raw materials and final inspection transformer as per standard specification sheet and IS/IEC Standards. Identification of the root cause of quality issues and execution of product quality improvements through preventive or corrective actions and to perform routine tests.} 
				%Continual improvement on product's Aesthetic look, Painting quality and other. To perform routine tests prior and after on each transformer in 	presence of Madhya Gujarat Vij Company Limited (Power Utility) board representatives.}
		\end{cvitems}
	}	
\end{cventries}